---
title: "assignment 7"
author: "Chen Ling"
format: html
editor: visual
execute: 
  echo: false 
  warning: false
  message: false
---

```{r }
library(googledrive)
library(tidyverse)
library(data.table) ## For the fread function
library(lubridate)
library(knitr)

source("sepsis_monitor_functions.R")
```

## task4

```{r}
drive_deauth()
file_link <- "https://drive.google.com/file/d/16CPL21wWAJoIAu6hVEAo4MJKByGpBhag/view?usp=share_link"
## All data up until now
new_data <- updateData(file_link)

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))

```

## Current date and time

```{r}
Sys.time()
```

## A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r}
q1<-most_recent_data%>%filter(SepsisLabel==1)%>%select(PatientID,HR,Temp,Resp)
kable(q1)
```

## Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU.

```{r}
q2=new_data%>%filter(SepsisLabel==1)
plothr<-ggplot(data=q2,aes(x=ICULOS,y=HR,color=PatientID))+
  geom_point()+
  geom_line()
plottemp<-ggplot(data=q2,aes(x=ICULOS,y=Temp,color=PatientID))+
  geom_point()+
  geom_line()
plotresp<-ggplot(data=q2,aes(x=ICULOS,y=Resp,color=PatientID))+
  geom_point()+
  geom_line()
plothr;plottemp;plotresp
```

## A table showing the change in heart rate, temperature, and respiratory rate between the last two measurements for all patients

```{r}
q3<-new_data%>%group_by(PatientID)%>%summarise(mean=mean(ICULOS))%>%filter(mean>0)%>%select(PatientID)
q31<-new_data%>%right_join(q3,by = "PatientID")%>%mutate(laghr=lag(HR),lagtemp=lag(Temp),lagresp=lag(Resp))%>%
  mutate(diffhr=HR-laghr,difftemp=Temp-lagtemp,diffresp=Resp-lagresp)%>%
  group_by(PatientID)%>%summarise_all(last)%>%select(PatientID,diffhr,difftemp,diffresp)
kable(q31)
  
```
